\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}

\usepackage[square,numbers]{natbib}
\bibliographystyle{unsrtnat}

\title{Google \texttt{Maps} }
\author{Michał Konarski and Wojciech}

\begin{document}
	
	\maketitle
	

\section*{Abstract}
Android studio is the official intergrated development environment for the google android operating system buit on jetbrain's intelliJ IDEA software.\cite{huddersfieldtpsamson}


\section*{Introduction}
Android Studio is designed specifically for android development android studio provides the fastest tools for buiding Apps on every type of Android device. 
\paragraph{}

World class code editing, debuging, performance tooling, a flexible build system, and an instant build allows people to focus on building unique and high quality apps. the new android emulators are faster than ever and allows you to dynamically resize the emulator and access a suite of sensor controls. Android studio also easily configures projects to include code libraries and generate multiple buid variants from a single project. with the Android studio cradle, android studio offers high peformance build automation, robust dependence management and customirized build configurations

\section*{Conclusions}
.\cite{Turk.J} NET technology based on Google Maps service, is not a difficult process. It is basically about the communication between JavaScript\cite{TownsedBaptiste} and. NET and it can be easily established with usage of a WebService, where data serialization is done automatically.\cite{Online}


	
	\medskip
	
	\bibliography{sample}
	
\end{document}
